New cardinality estimation algorithms for HyperLogLog sketches

### 2017-01-22 paper/paper.tex
minor change

\cref{alg:insert} has some properties which are especially useful for distributed data streams. First, the insertion order of elements has no influence on the final HyperLogLog sketch. Furthermore, any two HyperLogLog sketches with same parameters $(\symPrecision, \symRegRange)$ representing sets $\symSetA$ and $\symSetB$ can be easily merged. The HyperLogLog sketch that represents the union of both sets is simply constructed by taking the register-wise maximum values as demonstrated by \cref{alg:union}.

>>>>

\cref{alg:insert} has some properties which are especially useful for distributed data streams. First, the insertion order of elements has no influence on the final HyperLogLog sketch. Furthermore, any two HyperLogLog sketches with same parameters $(\symPrecision, \symRegRange)$ representing two different sets can be easily merged. The HyperLogLog sketch that represents the union of both sets can be easily constructed by taking the register-wise maximum values as demonstrated by \cref{alg:union}.
